fGFPCA dynamic prediction

### 2023-01-23 f-GFPCA.Rmd
try ssh
prediction interval

---
title: "fGFPCA dynamic prediction (In-sample)"
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 4
date: "2022-11-03"
---

@@

>>>>

---
title: "fGFPCA dynamic prediction"
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 4
date: "2022-11-03"
---

@@

### Prediction interval

With MLE of scores $\hat{\boldsymbol{\xi}}$

$$\boldsymbol{\hat{\eta}}=\boldsymbol{\hat{f_0}}+\boldsymbol{\Phi\hat{\xi}}$$
$$\begin{aligned}
\hat{\boldsymbol{\eta}}-\boldsymbol{\eta}&=\boldsymbol{\hat{f_0}}+\boldsymbol{\Phi\hat{\xi}}-\boldsymbol{\eta}\\
&= \boldsymbol{\hat{f_0}-f_0}+\boldsymbol{\Phi(\hat{\xi}-\xi)}-\boldsymbol{\epsilon}
\end{aligned}$$

$$Var(\hat{\boldsymbol{\eta}}-\boldsymbol{\eta})=Var(\boldsymbol{\hat{f_0}-f_0})+\boldsymbol{\Phi\Gamma \Phi^T}+\hat{\sigma_{\epsilon}}^2$$
Note:

- $\boldsymbol{\Gamma}$ is estimated from FPCA. $\hat{\boldsymbol{\xi}}$ is also derived conditional on this covariance matrix.
- <span style="color: red;"> ? Covariance of $\boldsymbol{\hat{f_0}-\eta}$ and $\hat{\boldsymbol{\xi}}$ should be 0 by assumption? </span>
- <span style="color: red;"> $Var(\boldsymbol{\hat{f_0}-f_0})$ should not change from in-sample prediction formula since it is only related to the FPCA part? </span>

$$Var(\boldsymbol{\hat{f_0}-f_0})=\boldsymbol{\Phi(H\Phi_m\Gamma)\Phi^T}$$

$$Var(\hat{\boldsymbol{\eta}}-\boldsymbol{\eta})=\boldsymbol{\Phi(H\Phi_m+I_K)\Gamma\Phi^T}+\hat{\sigma_{\epsilon}}^2\boldsymbol{I}_m$$
